The \dealii Library, Version 9.5

### 2023-06-29 9.5/paper.tex
Adjust spaces
Update funding for LH and MF.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/mesh_0.png}
  \end{subfigure}\qquad
  \hfill
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/mesh_1.png}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/mesh_2.png}
  \end{subfigure}
  \caption{\it Example of non-nested multigrid levels.\todo[inline]{Make gap uniform!}}\label{fig:nonnested}
\end{figure}

@@

\todo[inline]{Marco: Anything to add here?.}

@@

L.~Heltai was partially supported by the Italian Ministry of Instruction,
University and Research (MIUR), under the 2017 PRIN project NA-FROM-PDEs MIUR
PE1, ``Numerical Analysis for Full and Reduced Order Methods for the efficient
and accurate solution of complex systems governed by Partial Differential
Equations''.

>>>>

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/mesh_0.png}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/mesh_1.png}
  \end{subfigure}
  \hfill
  \begin{subfigure}[b]{0.28\textwidth}
    \centering
    \includegraphics[width=\textwidth]{png/mesh_2.png}
  \end{subfigure}
  \caption{\it Example of non-nested multigrid levels.}\label{fig:nonnested}
\end{figure}

@@

@@

L.~Heltai and M~.Feder were partially supported by the Italian Ministry of
University and Research (MUR), under the grant MUR PRIN 2022 No. 2022WKWZA8
``Immersed methods for multiscale and multiphysics problems (IMMEDIATE)''.
